---
title: "Cdogr"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Cdogr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Loading the package

Load `Cdogr` with:

```{r setup}
library(Cdogr)
```
# Introduction

`Cdogr` allows you to generate random DNA sequences, convert DNA to RNA, split RNA into codons, translate RNA codons to amino acids, and visualize the frequency of amino acids in a sequence.


# Functions in `Cdogr`

## 1. Generating a Random DNA Sequence

You can generate a random DNA sequence of a specified length with the 'Cdogr_seq()' function. The function takes 'size' of the desired DNA length as input.

```{r}
dna_sequence <- Cdogr_seq(30)
print(dna_sequence)
```

## 2. Converting DNA to RNA

You can convert a DNA sequence to RNA with the `Cdogr_substitution()` function. The input of the function is a DNA sequence.

```{r}
rna_sequence <- Cdogr_substitution(dna_sequence)
print(rna_sequence)
```

## 3. Splitting RNA into Codons

You can split an RNA sequence into its constituent codons with the `Cdogr_splitting()` function. The input is an RNA sequence and start parameter picks the reading frame.

```{r}
codons <- Cdogr_splitting(rna_sequence, start = 1)
print(codons)
```


## 4. Translating RNA Codons to Amino Acids

You can translate a sequence of RNA codons into amino acids with the `Cdogr_translating()` function.

```{r}
amino_acids <- translating(codons)
print(amino_acids)
```

## 5. Visualizing Amino Acid Frequencies

You can visualize the frequency of each amino acid in a sequence with the `Cdogr_frequencies()` function. The function uses the list of amino acids as input. 

```{r}
plot <- Cdogr_frequencies(amino_acids)
print(plot)
```
